\section{The Coffee \& Donut Shop}
\emph{effective August 19, 2018}\\

\subsection{Management Committee}
\subsubsection{Composition}
There shall be a C\&D Management Committee. The membership of the Committee shall
consist of:
\begin{itemize}
    \item The President;
    \item The Vice-President, Finances;
    \item The Vice-President, Operations;
    \item One person appointed by the Dean;
    \item One person appointed by the Vice President, Operations \& Finance of
        the Federation of Students; 
    \item The Business Manager;
    \item The manager of the C\&D; and
    \item Two additional members appointed by the Board of Directors.
\end{itemize}

The committee shall be chaired by either the Business Manager or the President.

The secretary of the Committee shall be appointed by the Committe at the start
of each term.

Quorum for the Committee shall be a majority of its members who serve as
Directors of the Society. Only those members shall be counted for determining
whether or not a quorum is present.

\subsubsection{Duties \& Powers}
The C\&D Management Committee is responsible to manage the C\&D, and generally
has the power necessary to do so, as well as to generally delegate that power
to any subcommittees or to members or employees of the Society, the Federation,
or the University. It has the power to set hiring policies in accordance with
University hiring process and direct the Human Resources Committee in regards
to employees of the C\&D.

The C\&D's bank account is combined with the Society's primary account,
but revenue, expense, and cash flow is tracked separately. 
The Committee shall have power to manage and spend funds within the managed cash
flow of the C\&D. 

The Committee shall meet as deemed necessary by the Board to 
address any major concerns. 

The Committee's decisions shall not conflict with any decision of the Society,
and it must follow instructions given to it by the Society. Its decisions are
subject to amendment or rescindment by superior bodies.

\subsection{Manager}
The Society shall hire a manager for the C\&D.

The manager of the C\&D shall be responsible for management of the C\&D under
the supervision of the Business Manager and the C\&D Management Committee and
shall generally have the power to manage its affairs, subject to the authority
of the Committee and other bodies of the Society.

\subsection{Capital Expenditures}
The C\&D Manager's authority to approve capital expenditures is limited to
a maximum of \$500. The manager and the Vice President, Operations can together
approve capital expenditures up to \$2000. The C\&D Management Committee can
approve capital expenditures up to \$5000. Larger amounts must be approved by
the Board of Directors.

\subsection{Catering}

\subsubsection{Catering Refusal}
Due to the nature of the C\&D's business and the size of C\&D facilities, catering services are not guaranteed.

\subsubsection{Order Placement}
The Mathematics Society and it's clubs and affiliates may request catering for events from the C\&D by placing an order with the Business Manager. 
The Mathematics faculty may also request catering, but whether or not the C\&D fulfills these orders is up to the discretion of Business Manager. 
The C\&D may choose to fulfill requests made by other organizations.
Inquiries and orders may be made in person, by email or by phone to the Business Manager.
Orders must be placed at least 2 business days prior to the event.
The Business Manager shall respond to requests within 12 hours of receiving them.

\subsubsection{Restrictions}
Orders with an expected attendance over 100 may be accommodated at the discretion of the Business Manager.
The C\&D shall fulfill requests made in compliance with this procedure by the Mathematics Society, or its clubs and affiliates. 
The C\&D shall fulfill requests made in compliance with this procedure by the Mathematics faculty and other organizations at the discretion of the Business Manager.

\subsubsection{Delivery}
Delivery is defined to be when the food is dropped off in the location discussed on the order.
Deliveries take place 15 minutes prior to the event provided the event occurs during C\&D business hours. 
Other delivery times may be discussed with the Business Manager.
The C\&D shall deliver food to events occurring in MC, M3, DC, and QNC.
Any other locations in close proximity may be discussed with the Business Manager at the time the order is placed.

\subsubsection{Exceptions to Catering}
If unable to provide delivery services, orders may be picked up from the C\&D the day of the catering is required. 
The pickup date and time must be discussed at the time the order is placed.

\subsubsection{Cancellation}
Cancellations may be made more than 2 business days prior to the event at no charge.
Cancellations made within less than 2 business days prior to the event may be charged for any special items ordered for the event.

\subsubsection{Liability}
The C\&D assumes no responsibility for the handling of the food after it is delivered or picked up.

\subsubsection{Billing}
The C\&D shall bill for catering services by sending invoices to the organization requesting catering.
If the Mathematics Society, or its clubs/affiliates have requested catering, the invoice shall be sent to the Mathematics Society.
If the Mathematics faculty has requested catering, they shall be sent an invoice.
Any other organizations requesting catering must provide payment at least 1 business day prior to the event where the catering is required.




