%%AMENDMENTS (a)
\section{Amendments}
Amendments to this document may be made by a referendum or by either:
\begin{enumerate}
    \item both a two-thirds majority vote of the Board of Directors and a
      two-thirds majority vote of Council, or 
    \item by a two-thirds majority vote of a general meeting, with notice.
\end{enumerate}

If an amendment is made by Council and the Board of Directors, then it can take
effect immediately (or as specified in a proviso), but it shall be subject to
confirmation by a general meeting. A general meeting may reject or confirm the
amendment. 

If rejected or if not confirmed by the end of the subsequent regular termly
general meeting, then the amendment is reversed and no subsequent amendment by
Council and the Board of Directors of similar substance has any effect until
confirmed at a general meeting. An amendment passed at a general meeting
implictly confirms similar amendments by Council and the Board of Directors.

\subsection{Contracts}
For the Society to enter into or assent to an amendment to a contract
that binds it for a duration of more than one term, it must be explicitly
approved by the Board of Directors.

External agreements entered into by the Society must be compliant with this
document and any relevant decisions of the Society. Additionally, unless it
terminates sooner, the Society can enter into an agreement only if it contains
a clause requiring that it be reviewed by the parties to it no less often than
once every four years.
