\section{Elections}
\begin{annotation}
    This section is fine to understand, but all sections relating to a specific
    position should be updated to be with those positions. As well, this 
    section is currently out of date with resolutions of past General Meetings.
    
    \textbf{Tristan Potter, Spring 2018}
\end{annotation}

All aspects of election procedure not defined explicitly in this document may be
set by a decision of the Society.

\subsection{General Election}
General elections shall be held each term for the subsequent term.

Elections shall be conducted using a preferential ballot system.

\subsection{By-elections}
In the event that one or more seats on Council or any of the elected executive
positions become vacant during or before the first month of a term, a by-election shall be held for those seats. If no by-election is held by the start of that
term, one shall be held as soon as possible after the term begins.

%% TODO Move the folowing to the relevent sections
\subsection{Elected Executive \& Upper-Year Reps}
For the Executive Officers other than the Appointed Executives and the
Representatives other than First Year and Software Engineering Representatives,
general elections shall be held in each term for the subsequent term. Elections shall be conducted using a preferential ballot system.

\subsection{Appointed Executives}
The following executives shall be appointed for each term by the Board
of Directors in the previous term:
\begin{enumerate} 
    \item the Vice-President, Finance;
    \item the Vice-President, Internal;
    \item the Vice-President, Communications; and,
    \item the Vice-President, Operations.
\end{enumerate}

\subsection{Election to Multiple Positions}
If a member is elected to both an Executive and a Representative seat
simultaneously, then they take the Executive seat and the votes cast in the
Representative election are reevaluated with the member disqualified. If a
Representative is elected to an Executive seat, then they lose their
Representative seat.
