%%OFFICERS ( ) 
\section{Officers}

The officers of the Society shall be:
\begin{enumerate}
    \item the President; 
    \item the Vice-President, Finance; 
    \item the Vice-President, Operations; 
    \item the Vice-President, Internal;
    \item the Vice-President, Academic;
    \item the Vice-President, Communications;
    \item the Chair of the Society;
    \item the Secretary of the Society; and,
    \item the Business Manager.
\end{enumerate}

The Officers of the Society shall serve until the term of the appointee is
concluded, or until their successor is elected. 

Each Officer shall perform the duties assigned to them by the bylaws, by the
policy and procedures of the Society, and by the Board of Directors.

No Officer shall approve funding to any organization in which they hold an
executive or similar position, unless such funding has explicitly been approved
by a decision of the Society.

\subsection{Executive Officers}
The Executive Officers of the Society shall be: \begin{enumerate}
    \item the President; 
    \item the Vice-President, Finance; 
    \item the Vice-President, Operations; 
    \item the Vice-President, Internal;
    \item the Vice-President, Academic; and,
    \item the Vice-President, Communications.
\end{enumerate}
An Executive Officer may not be a chairperson or executive member of a club or other 
organization receiving or petitioning to receive funds from the Society.

\subsubsection{Eligibility Requirements}
In order to serve as an Executive, a member must:
\begin{enumerate}
    \item be eligible to sit on the Board of Directors;
    \item be a math student; 
    \item have no other full-time non-academic commitments; and,
    \item have completed at least two terms of academic study.
\end{enumerate}

All of the Executive Officers are expected to attend regular meetings with
representatives of the Dean's office.

\subsubsection{Incapacitation}
\begin{annotation}
    The prevalence of Council as a deciding body on the incapacitation of 
    Executive Officers was done on purpose. Council should have significant
    power to declare executives as incapacitated if they are no longer
    serving students adequately, even if they may be serving the corporate
    interest of the Society. The Dean's Office is a neutral enough third party
    who can hear the case and determine an outcome.

    Appointees then come from Council or the Board of Directors should be from
    the recommendation supplied by the Executive

    \textbf{Tristan Potter, Spring 2018}
\end{annotation}

In the event that an Executive Officer becomes unable to fulfill their duties,
then three voting members of Council or the Board of Directors may,
with the written approval of the Dean or their designate, declare that Executive
Officer to be incapacitated. An Executive Officer may also declare themselves
to be incapacitated by written submission to the Board of Directors and
Council.

If an Executive Officer, is declared incapacitated or ceases to hold their
position for any reason, a decision of the Society shall appoint an interim
replacement. 

If the position of President or Vice President, Academic becomes vacant, it
is necessary for Council to make the appointment. Council shall convene
as soon as is practicable to do so, and the remaining Executive Officers, if
any, shall recommend a potential appointee at that meeting. If no quorate
meeting of Council may occur within the term, the Board of Directors may 
appoint a member to the vacant position.

If the position of any other Executive Officer becomes vacant, it is necessary
for the Board of  Directors to make the appointment. The Board of
Directors shall convene as soon as is practicable to do so, and the remaining
Executive Officers, if any, shall recommend a potential appointee at that
meeting.

If a voting member of Council or a Director is appointed as interim replacement
for an Executive Officer, then for the duration of the time that they serve as
interim replacement, their original powers and duties shall be suspended and,
if the replacement is themselves an Executive Officer, an interim replacement
shall be appointed for them and so on. For greater certainty, the duties and
powers referred to in this paragraph include those of being voting member of
Council and the Board of Directors, as is inherent in each of the Executive
Officer positions.

An Executive Officer may resume their duties by providing written notice to
Council and the Board of Directors at least three days in advance. A
notice by an Executive Officer declaring themselves to be incapacitated for a
fixed period of time counts as notice for this purpose. At the date specified
in the notice, unless indicated otherwise by an intervening written notice from
that Executive Officer, they resume their duties and powers. If their interim
replacement was another Executive Officer, then that Executive Officer resumes
their duties at the same time with no requirement of notice on their part.

\subsubsection{Remuneration of Executives}
As a form of compensation, each Executive Officer may receive an honorarium
for serving in a given academic term, provided that they have been in the role
for the majority of the term, are still in their role on the last day of the
term. This honorarium will be awarded through a single payment within
two weeks of the report on their performance being presented to the Board
of Directors. This does not preclude other non-monetary compensation. 

In the event that an Executive fails to effectively perform their duties,
a resolution by the Board of Directors may strip them of their
honorarium with a two-thirds vote, provided that the meeting occurs before the
payment is awarded. Debate on any such resolution will be held in confidential
session, without the presence of the Executive Officer(s) in question.

\subsection{Executive Board}

\subsubsection{Composition}
The Executive Board of the Society shall be composed of the Executive Officers
with the Business Manager serving as a resource member.

\subsubsection{Duties and Powers}
Each member of the Executive Board shall maintain at least three office hours
per week or be regularly available to students.

The Executive Board is responsible for performing all duties assigned to them
by a decision of the Society, and is accountable to Council and the
Board of Directors for the actions they take in performing their duties and
exercising their power.

The Executive Board is responsible for generally maintaining the affairs of the
Society between meetings of the Board of Directors, making recommendations to
Council and the Board of Directors for action, and ensuring that
decisions of the Society are implemented.  No action of the Executive shall
conflict with any decision of the Society.

The Executive Board is expected to send out regular communications to the
membership of the Society.

\subsection{President}
The President is the Chief Executive Officer of the Society, and shall:
\begin{enumerate}
  \item Represent the Society at official functions and public occasions;
  \item Work with external organizations on behalf of the Society;
  \item Where not provided otherwise by a decision of the Society, make
    appointments of members to external bodies on behalf of the Society, and in
    any case communicate the appointments to those bodies;
  \item Represent the Society and its members to other organizations;
  \item Attend meetings of the WUSA Committee of Presidents; and,
  \item Work with the other Executive to ensure that the transition from one
    term to the next goes smoothly.
\end{enumerate}

For greater certainty, the President need not seek election to external bodies
in order to satisfy the requirement that they represent the Society and its
members.

\subsection{Vice-President, Finance}
The Vice-President, Finance is responsible for the financial affairs of the
Society and shall:
\begin{enumerate}
  \item Prepare a budget, an opening financial report, and a closing financial
    report for the Society for each term and present them to Council; and
  \item Present up-to-date financial reports to termly general meetings.
\end{enumerate}

\subsection{Vice-President, Operations}
The Vice-President, Operations is responsible for the day-to-day operations of
the Society and shall:
\begin{enumerate}
  \item Oversee the services operated by the Society;
  \item Oversee the Society Office; and,
  \item Allocate and manage the use of any space allocated to the Society.
\end{enumerate}

\subsection{Vice-President, Internal}
The Vice-President, Internal is responsible for overseeing Society events and
shall:
\begin{enumerate}
  \item Serve as the final approver for all Society events, ensuring that all
      Society events have the appropriate documentation, including insurance
      coverage and/or event forms;
  \item Encourage members to become more involved in the Society and ensure
      that the opportunity exists for them to do so;
  \item Oversee all volunteers of the Society;
  \item Oversee all internal organizations on behalf of the society, including
      Clubs and Affiliates, ensuring they are supported in their endeavours and
      compliant with MathSoc policy and financial/accounting requirements;
  \item Meet with every club/service executive at least once each term;
  \item Ensure that volunteers within the Society are appropriately recognized
      for their efforts; and,
  \item Ensure that the spirit of Math does not leave the Society.
\end{enumerate}

\subsection{Vice-President, Academic}
The Vice-President, Academic is responsible for academic operations of the
Society and shall:
\begin{enumerate}
  \item Represent the Society and its members to the Faculty, to the University,
    and to the Federation of Students on academic issues;
  \item Ensure that members have access to up-to-date academic information;
  \item When changes are made to the programs offered by the Faculty, if
    necessary, suggest changes to the way that Council seats are allocated to
    accommodate the changes; and,
  \item In conduction with the other Executives, organize events and manage
    services of an academic nature.
\end{enumerate}

For greater certainty, the Vice-President, Academic need not seek election to
external bodies in order to satisfy the requirement that they represent the
Society and its members.

\subsection{Vice-President, Communications}
The Vice-President, Communications is responsible for the Society's 
communications and shall:
\begin{enumerate}
    \item Collaborate with the President for Society's official announcements and external
    communication;
    \item Oversee all postings on the Society's social media platforms;
    \item Oversee the marketing of the Society's events and services; and,
    \item Collaborate with the Vice-President, Operations on the information 
        provided on the Society's website.
\end{enumerate}

\subsection{Business Manager}
The Business Manager is responsible for the day-to-day operations of the 
Society, and shall:
\begin{enumerate}
    \item Manage the services operated by the Society;
    \item Manage the Society Office;
    \item Serve as a resource to the Executive Officers;
    \item Arrange suppliers for the Society and ensure that the Society is
        stocked in any supplies it needs;
    \item Provide organizational cohesiveness, continuity, and historical
        perspective;
    \item Oversee the human resource responsibilities of the Society;
    \item Oversee all of the daily financial aspects of the organization;
    \item Ensure the day-to-day financial security of the Society;
    \item Keep accurate and complete records of the finances of the Society;
    \item Manage the accounts and funds of the Society;
    \item Within two weeks of a request, present the financial records of the
        Society to any member;
    \item Assist in planning any term-scale initiatives; and,
    \item Provide input and guidance during transition periods.
\end{enumerate}

\subsection{Chair}
The Chair of the Society must be a current or Past Director.

The Chair has the following duties:
\begin{enumerate}
    \item Serve as the presiding officer of the Board of Directors;
    \item Interpret this and any other governing documents of the Society,
        subject to appeal to Council or a general meeting;
    \item Serve as a resource to the other Directors;
    \item Arrange for and advertise meetings of the Board of Directors;
    \item Ensure that all Directors have access to the official notice
        forum, if any; and,
    \item Ensure that meetings of the Board of Directors are called regularly.
\end{enumerate}

In the event that there is no Chair, the President shall assume the duties and
responsibilities of the Chair of the Society. 

\subsection{Secretary}
The Secretary has the following duties:
\begin{enumerate}
    \item Ensure a secretary is present at all meetings of Council,
        the Board of Directors, and general meetings;
    \item Record attendance of Council, Board of Directors, and
        general meetings, including when a member is more than one half-hour
        late for a meeting and if they sent notice of their absence;
    \item Distribute minutes of Council, the Board of Directors, and 
        general meetings in a timely manner;
    \item Absent a decision to the contrary by the assembly, serve as the
        secretary of general meetings;
    \item Report to Council and the Board of Directors when a Councillor
        or Director is failing to meet the requirements of office; and
    \item Maintain and update the official copies of this document and any other
        vital documents of the Society, including internal policies and external
        agreements.
\end{enumerate}

In the event that there is no Secretary of the Society, the Vice President,
Academic, shall assume the duties and responsibilities of the Secretary of the
Society.
