\section{Executive Appointment Committees}
\emph{effective 2020}\\

The Board is responsible for the appointment of the Vice-President of Internal, Vice-President of Operations and, Vice-President of Finance.  
The selection process for each of the appointed executive is governed by their respective appointment Committee. 

\subsection{Composition and Selection of Members}
The membership of the committee shall be:
\begin{enumerate}
    \item One (1) currently sitting members of MathSoc Board;
    \item One (1) currently sitting members of MathSoc Council; and
    \item Business Manager.
\end{enumerate}

The committees shall be chosen the term before the term of the executive in question. 
The committee shall convene no later than the 2nd month of the term and the applications shall be open to the public no later than the 3rd month of the term.

\subsection{Meetings}
The committees will meet on a need by need basis and shall be considered confidential unless deemed otherwise by the committee membership. 
No non-members of the committee may attend meetings unless explicitly invited by the committee to do so.
The quorum for the meetings shall be two thirds ($\frac{2}{3}$) of the committee members.

\subsection{Powers and Duties}

The committees shall: 
\begin{enumerate}
    \item Be responsible for opening and marketing applications to the public;
    \item Interview the candidates they deem necessary; and
    \item Report on the candidates and their interviews, as well as provide their recommendation to the Board of Directors. 
\end{enumerate}

\section{Appointment of Directors}
\subsection{Overview}
\subsubsection{Purpose}
This procedure:
\begin{enumerate}
    \item Provides a process for students at-large to apply and be considered for a seat on the 
        Board of Directors for the upcoming governing year elaborating and expanding on By-law Article 6, 
        Board of Directors.
    \item Provides additional guidance on handling vacancies on the Board that may arise. 
\end{enumerate}

\subsubsection{Application}
This procedure shall supplement the relevant bylaws and policies of the MathSoc. 
In case of a discrepancy between this procedure and the bylaws or policies,the bylaws and their policy interpretation shall prevail.

\subsection{Basic Requirements for Directors}
Applicants are expected to be full voting members of the Society (as defined in the bylaws) and expect to remain so for the term of their office.

\subsection{Election as a General Meeting}
\begin{enumerate}
    \item The Chair of the Board will advertise the available Director positions, collect applications
        and produce a summary report to be forwarded to the President. 
    \item The report shall be published alongside the General Meeting agenda; the Chair of the Board
        shall include a list of names of candidates deemed eligible based on those basic requirements 
        established in §B under the appropriate agenda item and on all forms of proxy.
    \item When the Election of Directors is reached in the agenda of the General Meeting:
    \begin{enumerate}
        \item The qualified candidates listed in the report shall be nominated by the chair of the General Meeting. 
            At-large candidates shall each be nominated for election to their respective seats.
        \item It shall be assumed that the candidates in question accept their nomination. 
            However, candidates may withdraw their nominations prior to the issuance of a ballot for the election of Directors.
        \item The chair of the General Meeting shall allow each qualified candidate to present a brief oral 
            summary of their qualifications for becoming a director on Board.  
            Candidates unable to attend in person may submit a brief summary to be read by the 
            chair of the General Meeting.
        \item Discussion shall then open to all present.
        \item Once there is no more discussion (or a Motion to Call the Question has passed), a vote will be held by secret ballot.

        \begin{enumerate}
            \item Each member (including Councillors) shall be entitled to a ranked ballot to vote for the At-large seats. 
                Members shall elect from amongst the candidates nominated by the Panel to be At-Large Directors.
            \item Those voting may rank as few or as many candidates as they desire. 
                Ballots shall be counted according to the Single Transferable Vote system. 
            \item Under no circumstances shall it be considered a conflict of interest for a candidate 
                to vote in an election in which they are a candidate.
        \end{enumerate}
        \item In the event that there are fewer than or an equal number of candidates to the 
            number of available seats, the chair of the General Meeting shall call for a 
            confirmation vote of the screened applicants.
        \begin{enumerate}
            \item Subsequently, the chair of the General Meeting may open the floor 
                for nominations for the remaining position(s).
            \item Otherwise, the chair of the General Meeting may recommend the assembly not 
                nominate any parties for the remaining position, and to allow the vacancy or 
                vacancies to be filled in accordance with the vacancy processes such that 
                any interested student may apply.
        \end{enumerate}
        \item Once the results of the count are announced by the chair, the motion to elect 
            the Directors shall be read with the names of the successful candidates 
            and then confirmed with a final vote. 

    \end{enumerate}
\end{enumerate}

\subsection{Handling of Vanacies on Board}

If an At-large Director seat becomes vacant, the seat shall be filled according to such processes determined by the Board of Directors, pursuant to the Bylaws and Policies of the Society.
When at-large seats are available for election for less than 12-months terms (due to vacancies arising part way through a term), an election shall first occur for the shorter term seats followed by an election for the one-year term seats.
If an at-large seat becomes temporarily inactive due to the holder becoming an Executive Officer, Council will be tasked to recommend a candidate to fill the position on a pro-tempore basis after publicising the vacancy.




