\section{Lounge and Hallway Bookings}
\emph{effective June 26, 2024; replaces June 4, 2024; replaces April 4, 2019; replaces August 19, 2018}\\

The Mathematics Society follows booking procedures in accordance with
University Policy 15, Bookings, Use and Reservation of University Facilities
for Activities Not Regularly Timetabled.

The lounges, MC 3001, MC 3002, MC 3028, and the hallway outside the lounges may be
booked by any organizations in group A, any group in class B,C or D with the approval of the Executive Board, and any group in class E with the approval of the University’s Booking Office, the Dean’s Office or an Associate Dean of the Faculty, and the approval of the Executive Board.

\subsection{Booking Groups}

The following booking groups were outlined in University Policy 15 on
August 14, 2018.

\begin{description}
	\item[A: Accredited Undergraduate Student Groups] Organized groups of students
		whose membership and constitution have been approved by the Federation of
		Students.

	\item[B: Accredited Graduate Student Groups] Any graduate student group
		approved by the Graduate Student Association.

	\item[C: Accredited University Groups] All departments of the University,
		research groups, Federated \& Affiliated Colleges, and any group, club or
		organization recognized by the University or its Federated \& Affiliated
		Colleges. In the case of the University, the Secretary of the University
		will determine status.

	\item[D: Community Charitable Organizations] Organizations such as the K-W
		Rotary Club, Lions Club, Children's International Summer Village, and
		others as approved by the Secretary of the University.

	\item[E: Non-accredited Student and Off-campus Groups] Organized groups which
		do not fall under A. to D. above.
\end{description}

\subsection{Booking Times}

\noindent The Comfy lounge (MC 3001) may be booked between the following hours:
\begin{enumerate}
	\item 6:00 pm to 2:00 am---Monday to Friday;
	\item 8:00 am to 2:00am---Saturday and Sunday;
	\item Any time at the discretion of the Executive Board.
\end{enumerate}

\noindent The C\&D lounge (MC 3002) may be booked between the following hours:
\begin{enumerate}
	\item C\&D Closing to 2:00 am---Monday to Friday;
	\item 8:00 am to 2:00 am---Saturday and Sunday;
	\item Any time at the discretion of the Executive Board.
\end{enumerate}

\noindent MC 3028 may be booked between the following hours:
\begin{enumerate}
	\item During the hours of operation of the MathSoc Office
	\item Any time at the discretion of the Executive Board
\end{enumerate}

\noindent The hallway may be booked between the following hours:
\begin{enumerate}
	\item 9:00 am to 5:00 pm---Monday to Friday;
	\item Any time at the discretion of the Executive Board.
\end{enumerate}

\noindent Only one lounge or hallway spot may be booked by the same organization at one
time, except under special circumstances, at the discretion of the Executive
Board.

\subsection{Booking Procedures}

A booking request should be completed in its entirety by a representative of the organization
making the booking. This representative shall be held responsible for the rented space for the
duration of the rental period. Any organization not affiliated with MathSoc will also be required
to entrust the Executive Board with a \$50 security deposit. The request and the deposit drop off
must be made at least 48 hours before the start of the event. This security deposit will be
returned to the borrower upon the end of the event except in the following cases:.

\begin{itemize}
	\item If the rented space is not returned to its initial state, satisfactory to the Executive Board
	\item If the rented space or items within it is damaged directly or indirectly by their occupation
	      of the space.
\end{itemize}

If the space is not cleaned or damage occurs, the organization will be charged for any costs
incurred.
Additionally, the booking rights of the organization, at the discretion of the Executive Board,
may be suspended for up to four (4) months following the incident. 

For organizations that are not affiliated with MathSoc, the Comfy Lounge or the Math CnD may be 
booked 3 times per term and the 3rd floor hallway may be booked 5 times per term. These limits may 
be waived at the discretion of the Vice President, Operations and one other member of the Executive Board. 

If the booking organization is not present in the space 30 minutes after the start of the booking time, 
their booking for the day shall be considered withdrawn and a warning will be issued. If the same 
organization is late again during that term, their right to book space, at the discretion of the Executive 
Board, may be suspended for up to four (4) months following the incident.

\section{Equipment Bookings}
\emph{effective July 26, 2023; replaces August 2018}\\

Any piece of equipment in the following list, or any other available equipment,
may be booked by any organizations in group A under University Policy 15, any
group in class B, C or D with the approval of the Executive Board, and any
group in class E with the approval of Council.

\begin{itemize}
	\item Projector (and projector screen)
	\item Speakers and microphone
	\item Canon camera
	\item Board games
\end{itemize}

Items on this list may only be borrowed by MathSoc clubs and affiliates:

\begin{itemize}
	\item Popcorn machine
\end{itemize}

The equipment borrower must be a student or staff member in the Faculty of Mathematics.

\subsection{Booking Procedures}

A booking request should be completed in its entirety by a
representative of the organization making the booking. Any organization not
affiliated with MathSoc will also be required to entrust the Executive Board
with a \$50 security deposit. The request and the deposit drop off must be made
at least 48 hours before the start of the event.

This security deposit will be returned to the borrower upon return of all the
equipment except in the following cases:

\begin{enumerate}
	\item If there is loss of equipment or damage to any equipment that would cause it to not function
	      properly. Should this be the case, the booking organization will be
	      responsible for reimbursing MathSoc for the full cost of the item.
	\item If the equipment is not returned properly and fully cleaned, at the
	      discretion of the Executive Board. In the case of MathSoc clubs, who do not
	      pay a deposit, a \$50 cleaning fee will be charged.
\end{enumerate}

The borrower agrees to be the sole operator of the equipment, or to be present
at all times during its use. The borrower agrees to return equipment in the same condition as it was rented out. Failure to do so may result in future booking privileges being revoked.

For organizations that are not affiliated with MathSoc, any equipment,
collectively, may be booked 5 times per term. (i.e. All pieces of equipment
share the same allowed use count for the term). This limit may be waived at the
discretion of the Vice President, Operations and one other member of the
Executive Board.

