\section{Central Budget}
\emph{Effective March 6, 2007; November 27, 2006}\\

\subsection{Approval of the Budget}
\begin{enumerate}
    \item The Vice-President, Finances shall present an operating budget to
        Council for approval by the end of the first month of each term. The
        central budget shall include a statement of accounts held by the
        society.
    \item All budget requests shall be submitted to the Vice-President,
        Finances, no later than the third week of the term.
    \item If funding from a previous term was allocated but has not yet been
        spent, it is forfeit unless mentioned in a budget request for the
        current term.  Council shall not refuse funding on a carry-over item
        that was allocated in either of the previous two terms, but may choose
        to reallocate the funds afterwards.
    \item First Year Representatives are excused from the first budget meeting
        of the Fall semester.
\end{enumerate}

\subsection{Funding Carry-Over}
\begin{enumerate}
    \item If funding from a previous term was allocated but has not yet been
        spent, it is forfeit unless mentioned in a budget request for the
        current term. Council shall not refuse funding on a carry-over item
        that was allocated in either of the previous two terms, but may choose
        to reallocate the funds afterwards.
    \item Funds in the Society's main accounts shall be included in the budget
        in each term as available funds, except for expenses that have been
        approved but that have not yet been reimbursed.
    \item \$10,000 shall be maintained in the Society's main accounts as a
        float.
\end{enumerate}

\subsection{Approval of Expenses}
\begin{enumerate}
    \item All non-budgeted expenses must be approved by members of the
        Executive Board or the Society Council as follows.
        \begin{enumerate}
            \item For expenses under \$20.00, the approval of a single member
                of the Executive Board is required;
            \item For expenses between \$20.00 and \$100.00, the approval of
                two members of the Executive Board, one of which must be the
                Vice-President, Finances, is required.
            \item Council must approve all expenditures over \$100.00.
        \end{enumerate}
    \item Budgeted expenditures must be approved by the appropriate member of
        the Executive Board. The Vice-President, Finances, must be informed of
        the approval as soon as possible. They shall not exceed the budgeted
        amount without approval from Council.
    \item The Vice-President, Finances shall report expenditures over the
        budgeted amount to Council.
    \item No expense shall be approved from a previous term's budget after the
        budget meeting for a term unless the unallocated funding was reported
        and approved in the central budget in the current term.
\end{enumerate}

\subsection{Reimbursement}
\begin{enumerate}
    \item Expenses incurred in the course of organizing, planning, and
        executing items of business for the Society are recoverable as long as
        the conditions in policies are met.
    \item All expense requests must be accompanied by a receipt to be approved.
    \item A record of expenditures to be reimbursed are to be submitted to the
        Executive Board within one week following the event. If exact values
        for the event are not known, an upper estimate should be provided
        immediately, and an event summary will be provided with appropriate
        figures as soon as possible. If this is not complied with the
        expenditure may not be reimbursed.
\end{enumerate}

\subsection{Income}
\begin{enumerate}
    \item Income earned in the course of executing society business shall be
        counted and recorded on an appropriate income form and submitted to the
        VPF.
\end{enumerate}
