\section{The Coffee \& Donut Shop}
\emph{effective August 19, 2018}\\

\subsection{Management Committee}
\subsubsection{Composition}
There shall be a C\&D Management Committee. The membership of the Committee shall
consist of:
\begin{itemize}
    \item The President;
    \item The Vice-President, Finances;
    \item The Vice-President, Operations;
    \item One person appointed by the Dean;
    \item One person appointed by the Vice President, Operations \& Finance of
        the Federation of Students; 
    \item The General Manager;
    \item The manager of the C\&D; and
    \item Two additional members appointed by the Board of Directors.
\end{itemize}

The committee shall be chaired by either the General Manager or the President.

The secretary of the Committee shall be appointed by the Committe at the start
of each term.

Quorum for the Committee shall be a majority of its members who serve as
Directors of the Society. Only those members shall be counted for determining
whether or not a quorum is present.

\subsubsection{Duties \& Powers}
The C\&D Management Committee is responsible to manage the C\&D, and generally
has the power necessary to do so, as well as to generally delegate that power
to any subcommittees or to members or employees of the Society, the Federation,
or the University. It has the power to set hiring policies in accordance with
University hiring process and direct the Human Resources Committee in regards
to employees of the C\&D.

The C\&D shall have a separate bank account from the Society's primary account,
and the Committee's power to manage and spend funds shall be limited to that
account.

The Committee shall meet at least once in each month in which there are at
least three weeks of classes, and shall report to the Board at least once each
term.

The Committee's decisions shall not conflict with any decision of the Society,
and it must follow instructions given to it by the Society. Its decisions are
subject to amendment or rescindment by superior bodies.

\subsection{Manager}
The Society shall hire a manager for the C\&D.

The manager of the C\&D shall be responsible for management of the C\&D under
the supervision of the General Manager and the C\&D Management Committee and
shall generally have the power to manage its affairs, subject to the authority
of the Committee and other bodies of the Society.

\subsection{Capital Expenditures}
The C\&D Manager's authority to approve capital expenditures is limited to
a maximum of \$500. The manager and the Vice President, Operations can together
approve capital expenditures up to \$2000. The C\&D Management Committee can
approve capital expenditures up to \$5000. Larger amounts must be approved by
the Board of Directors.

