\section{Conflict of Interest}
\emph{effective May 1, 2019}\\

\subsection{Definition}
A Director shall be considered to have an actual, perceived, or potential conflict of interest when the opportunity exists for the Director to use the authority, knowledge, or influence of the Mathematics Society Board of Directors, or a committee or body thereof, for individual benefit or to preferentially benefit any individual or organization with whom the Director has a familial, personal, fiduciary, or financial relationship.

\subsection{Candidates}
All Directors and Executives shall be expected to certify, prior to candidacy for election or appointment, that if elected they shall fulfil the responsibilities outlined in this procedure. Failure of a candidate for the Board of Directors or Executive to certify the same shall render the individual ineligible for candidacy.

\subsection{Declaration of Conflict}
All Directors will be required to complete and submit a Conflict of Interest Declaration, which will be in congruence with the requirements of this procedure, to the Chair of the Board upon their election or reelection to the Board of Directors. 

\subsubsection{Declaration Deadline}
Directors and Executives must submit the form no later than the first Board meeting of their term.

\subsubsection{Councillor Representatives}
For executives and other Directors that are also on Council, this required form shall be in addition to and separate from any requirements to submit conflicts of interest forms to Council.

\subsubsection{New Conflicts}
In the event that new conflicts of interests arise during the course of a Director’s or executive’s term, Directors and executives are responsible for ensuring their Conflict of Interest Declaration remains up to date.

\subsection{Availability of Declarations}
The Society Secretary shall ensure that copies of all submitted Conflict of Interest Declarations are available for inspection by any member of MathSoc during any Board meeting. Additionally, the Secretary shall make arrangements upon request for a member of MathSoc unable to attend a Board meeting to instead view the documents (without being able to preserve copies of it) at the MathSoc office.

\subsection{Conflicts in Meetings}
Directors who have an actual, perceived, or potential conflict of interest, with respect to any matter under consideration by Board, a MathSoc General Meeting, or a committee or body thereof, shall declare the nature and extent of the interest immediately and refrain from taking part in any vote in relation to the matter.

\subsection{Undeclared Conflicts}
When the Board, or a committee or body thereof, is of the opinion that a conflict of interest exists that has not been declared, the Board, a MathSoc General Meeting, or the committee or body thereof may declare by resolution, carried by two-thirds of its members present at the meeting, that a conflict of interest exists and the Director thus declared to be in conflict refrain from taking part in any discussion or in any vote in relation to the matter.
