\section{Decisions Between Meetings}
\textit{effective October 23, 2021}

\subsection{Overview}
Often striking a balance between reasonable oversight and micromanagement can be difficult. In the past, Board meetings have been called to approve several small, non-controversial yet urgent items. This procedure shall be used to determine which decisions may be made between meetings of the Board. The process through which these decisions are made are determined through applicable procedure(s).

\subsection{Definitions}
\begin{itemize}
    \item \textbf{"Away Vote (A-Vote)"} in the context of this policy shall mean the action of making a decision between meetings of the Board. 
    \item \textbf{"Away Decision (A-Decision)"} shall mean the outcome of an A-Vote.
\end{itemize}

\subsection{Applicability of A-Votes}

\subsubsection{General}
This procedure shall apply to urgent, non-controversial items, normally with a financial commitment of less than \$500 each.

\subsubsection{Veto}
Any Director entitled to a vote may veto an A-Vote; however, an A-Decision shall be binding, pending ratification at a subsequent Board meeting.
\textit{Note: Ratification is not withheld unless there is a concern where due process was not followed. Ratification must not be withheld solely due to distaste with the outcome of a vote.}

\subsubsection{Abuse}
An A-Vote which fails or is forced to be withdrawn shall not be brought again for an A-Vote in the same governing term unless otherwise determined at a meeting with due authority.

An A-Vote may not be held:
\begin{enumerate}
    \item to suspend procedure or policy;
    \item to allow another A-Vote under any circumstance;
    \item to pass any motion which should be held by secret ballot;
    \item by secret ballot;
    \item to pass any motion which contradicts any decision of the society at a general meeting; or
    \item to pass any motion which contradicts any decision of the society in the last year.
\end{enumerate}

\subsection{Due Process for A-Votes}

\subsubsection{Initialization}
An A-Vote may be called by any person(s) entitled to call a meeting of the Board. An A-Vote is considered initialized when notice has been sent, in the same method by which notice for a meeting of the Board would normally be sent. As with a motion submitted to a meeting of the Board, an A-Vote requires a mover and seconder.

\subsubsection{Veto}
Any voting member of the Board may veto an A-Vote. This may be done by sending a written request to the Chair of the Board within twenty-four (24) hours of the A-Vote being initialized.

\subsubsection{Timeline}
When initialized, a twenty-four (24) hour question and answer period will begin.  At the end of this period, all questions shall be compiled, responded to by either the mover or seconder, and reported to the entirety of the Board. After responses are submitted, a twelve (12) hour voting period shall begin.

\subsubsection{Voting and Threshold}
An A-Vote shall pass by a three-quarters ($\frac{3}{4}$) majority. A motion that does not meet the prescribed threshold but would pass with a majority does not fail, but is forced to be withdrawn. A motion forced to be withdrawn is automatically brought to the next meeting of the Board to be voted upon.