\section{Appointment of Directors}
\subsection{Overview}
\subsubsection{Purpose}
This procedure:
\begin{enumerate}
	\item provides a process for students at-large to apply and be considered for a seat on the
	      Board of Directors for the upcoming governing year elaborating and expanding on Bylaw Article 6,
	      \textit{Board of Directors}, and
	\item provides additional guidance on handling vacancies on the Board that may arise.
\end{enumerate}

\subsubsection{Application}
This procedure shall supplement the relevant bylaws and policies of the MathSoc.
In case of a discrepancy between this procedure and the bylaws or policies, the bylaws and their policy interpretation shall prevail.

\subsection{Advance Nominations}
To allow for candidates who are unable to attend the General Meeting to run for at-large seats, advance nominations will be allowed up to 24 hours before the General Meeting begins.
Advance candidates may submit a proxy to the chair of the General Meeting who is entitled to answer questions on their behalf if the candidate is unable to attend the meeting.
All eligible advance candidates are entitled to a blurb to be included in the agenda and shown to attendees as long as the following conditions are met:
\begin{enumerate}
	\item the blurb is under 100 words;
	\item the blurb is submitted at least five business days before the termly General Meeting; and
	\item the candidate states which election(s) that they are interested in running in.
\end{enumerate}
If a candidacy and/or blurb is submitted less than five business days before the General Meeting but more than 24 hours before the General Meeting begins, the chair of the General Meeting shall present these as they see fit during the at-large seat nomination period.

\noindent Advance nominations shall be treated equally to nominations made at the General Meeting.

\subsection{Handling of Vanacies on the Board}
\subsubsection{Due to becoming an Executive Officer}
If the holder of an at-large seat is announced to be an Executive Officer the following term before the termly General meeting, an at-large seat with a term of 4 months will be elected at the General Meeting.
If the announcement comes after the termly General Meeting, Council will be tasked to recommend a candidate to the Board of Directors, to fill the position on a pro-tempore basis after publicising the vacancy.

\subsubsection{Order of Elections}
Elections for at-large directors shall be done first for the term of longest length that is unfilled.
This process should repeat until all possible elections for vacancies have been held.
