\section{Equipment Bookings}
\emph{effective November 28, 2024; replaces July 26, 2023; August 2018}\\

Any piece of equipment in the following list, or any other available equipment,
may be booked by any organizations in group A under University Policy 15, any
group in class B, C or D with the approval of the Executive Board, and any
group in class E with the approval of Council.

\begin{itemize}
	\item Projector (and projector screen)
	\item Speakers and microphone
	\item Board games
\end{itemize}

Items on this list may only be borrowed by MathSoc clubs and affiliates:

\begin{itemize}
	\item Popcorn machine
	\item Nikon camera
	\item Canon camera
\end{itemize}

The equipment borrower must be a student or staff member in the Faculty of Mathematics.

\subsection{Booking Procedures}

A booking request should be completed in its entirety by a
representative of the organization making the booking. Any organization not
affiliated with MathSoc will also be required to entrust the Executive Board
with a \$50 security deposit. The request and the deposit drop off must be made
at least 48 hours before the start of the event.

This security deposit will be returned to the borrower upon return of all the
equipment except in the following cases:

\begin{enumerate}
	\item If there is loss of equipment or damage to any equipment that would cause it to not function
	      properly. Should this be the case, the booking organization will be
	      responsible for reimbursing MathSoc for the full cost of the item.
	\item If the equipment is not returned properly and fully cleaned, at the
	      discretion of the Executive Board. In the case of MathSoc clubs, who do not
	      pay a deposit, a \$50 cleaning fee will be charged.
\end{enumerate}

The borrower agrees to be the sole operator of the equipment, or to be present
at all times during its use. The borrower agrees to return equipment in the same condition as it was rented out. Failure to do so may result in future booking privileges being revoked.

For organizations that are not affiliated with MathSoc, any equipment,
collectively, may be booked 5 times per term. (i.e. All pieces of equipment
share the same allowed use count for the term). This limit may be waived at the
discretion of the Vice President, Operations and one other member of the
Executive Board. All equipment from the above list must be returned to the Vice President, 
Operations within 24 hours after the event, unless explicit written authorization has been 
granted by the Vice President, Operations for an extension. 
