\section{Executive Evaluation Committee}
\emph{effective June 26, 2024; replaces August 19, 2018; replaces March 25, 2014}

\subsection{Composition and Selection of Members}
The membership of the committee shall be:
\begin{enumerate}
	\item Two (2) currently sitting members of MathSoc Board;
	\item Two (2) currently sitting members of MathSoc Council;
	\item One representative from the Dean's Office as a non-voting member; and
	\item Business Manager.
\end{enumerate}

One of the two sitting Board members shall be assigned as the Chair of the Committee.
One of the four (4) full members of the Society is required to be a past Executive of the Society.

All members shall serve on the committee from the first day of an academic
term, until the last day of that term.

All members, save for the members of Council and the representative of the
Dean, shall be appointed to the committee by the Board of Directors of the
Society, prior to the start of the academic term in question. The members of
Council shall be appointed to the committee by MathSoc Council in its first
meeting of the term. The representative of the Dean's Office shall be chosen by
the Dean.

In the event that a committee member resigns or does not respond, the Chair of the committee, in collaboration with the governing body the committee member was a part of, shall have the power to hold an away vote to find a suitable replacement from Council or Board representatives

No current Executive may sit on the committee.

\subsection{Meetings}

All meetings of the committee shall be considered confidential, unless deemed
otherwise by the committee membership. No non-members of the committee may
attend meetings, unless explicitly invited by the committee to do so.

Quorum for the meetings shall be two thirds (2/3) of the committee members.

\subsection{Powers and Duties}

The committee shall:
\begin{itemize}
	\item Follow and recommend updates to Council Policy 25 (Executive
	      Evaluation Criteria) as a set of objective metrics for use in
	      evaluating Executive performance;
	\item Evaluate the current Executive against these metrics, meeting with
	      them, in person, at least twice during their term;
	\item Report the overall findings of these evaluations to the Board of
	      Directors; and
	\item Provide a confidential report to each Executive, detailing feedback
	      and recommendations for improvement.

\end{itemize}

\subsection{Confidentiality and Information Retention}

All files of the committee are considered confidential; they may only be viewed by current members of the committee,
unless the committee determines that there is a specific and identifiable need for a particular individual not sitting on the committee to access a certain file or a subset of the information contained therein.
Reports, evaluations, and all associated files must be destroyed no more than five calendar years after their completion.

