\section{Key Distribution}
\emph{effective August 19, 2018}\\

The distribution of keys/fobs to any offices controlled by the Society must be
approved in writing by the President or the Vice President, Operations before
approval from the Faculty is sought. The Vice President, Operations shall act
as key controller for the Society. Executive Members of the Society shall not
be allowed to sign out their own keys/fobs. Authority for keys/fobs is granted
by the Faculty, and keys/fobs may be refused by the Faculty even if authorized
by MathSoc.

Keys/fobs must be returned to the Faculty before or on the date indicated on
the form used to obtain the key/fob. Upon resignation of any key-holding
position within the Society, the permit for the keys associated with this
position expires immediately, and the keys/fobs shall be immediately and
properly returned. If any evidence of misuse by an individual has occurred, as
determined by the Executive Board or the Faculty, all keys/fobs must be
returned immediately to the Faculty. Any individual who fails to return all of
their keys/fobs on time will not be permitted to hold any keys/fobs controlled
by the Society for a period of 8 months; this may be appealed at the Board of 
Diretors.

\subsection{Core Key-holding Positions}
The following positions within the Society may request to hold keys relating to
their positions, as stated below:
\begin{enumerate}
    \item The President---A master key and master fob, allowing access to all
        Society offices in case of emergency. This key should also unlock the C\&D
        and Comfy Lounges.
    \item All other Executive Members---A sub-master key, allowing access to the
        Society Main Office, Executive Office, and the Society storage room.
    \item The Novelties Director---A key allowing access to the Society Main
        Office, and a key allowing access to the Society storage room.
    \item The Games, Computing, Marketing Directors, the Chief Returning Officer,
        Speaker, Secretary and the Finance and Accounting Assistants---A key
        allowing access to the Society Main Office.
    \item The Business Manager---A sub-master key, allowing access to the Society
        Main Office, Executive Office, their office, the Society Main Office, and
        the Society storage room.
    \item Other director positions with unanimous consent of the
        Executive Board.
\end{enumerate}

\subsection{Club Key-holding Positions}
Each club that is officially recognized as part of the Society and whose keys
are administered by MathSoc may request up to a maximum of 5 keys/fobs to their
club office for their executive members. These keys/fobs are non-transferable
and should not be used by more than one person, and must immediately be
returned to the Faculty on or before the end of the expiration period. In
addition, the President of each club may request one key that allows access to
the Society Main Office.

\subsection{Other Key-holding Positions}
The following may request the following keys/fobs:
\begin{enumerate}
  \item Women in Math Committee---up to 5 key/fobs allowing access to their
    office and one key that allows Society Main Office, to be held by the chair
    of the committee.
  \item Math Graduation Committee---up to 2 keys allowing access to their
    office and up to two keys that allow access to the Society Main Office.
  \item Math Orientation Committee---up to 5 keys allowing access to their
    office and up to 5 keys that allow access to the Society Main Office.
  \item The Waterloo Science Fiction Club---One key that allows access to the
    Society Main office, to be held by their appointed MathSoc key holder, in
    accordance with the MathSoc/WatSFiC agreement.
  \item mathNEWS---up to 5 keys allowing access to their office and up to 5
    keys that allow access to the Society Main Office
  \item Mathematics Endowment Fund---One key allowing access to their office
    and one key that allows access to the Society Main Office
  \item Coffee and Doughnut Shop Manager---One key allowing access to their
    office, one key allowing access to the Coffee and Doughnut Shop, and one
    key allowing access to Society Main Office.
\end{enumerate}
