\section{Locker Distribution}
\emph{effective August 19, 2018; replaces Council Policy---Locker Distribution
    effective July 17, 2014; replaces December 4, 2002; replaces March 23,
    1999}\\

Each member of the Society may use one locker per term, subject to
availability. Additionally, the lockers may be used by non-Society members,
only available for registration on the first day of the second month of
classes.

\subsection{Locker Booking}
These lockers shall be available for registration on the MathSoc website and
the booking system shall remain open from the second week of class until all
lockers have been occupied.

Upon request for a locker, the member will be randomly assigned a locker number
and the appropriate combination. Once being issued the combination for the
locker, the member may no longer change or revoke their own booking for the
term. The booker also agrees to be the sole occupier of the locker at all
times.

\subsection{Locker Administration}
No later than the beginning of the second week of classes each term, the Vice
President, Operations shall be tasked with resetting the lockers. This entails:

\begin{enumerate}
    \item Changing each locker combination in accordance with privacy and security
        guidelines.
    \item Removing the contents of each locker, storing and labelling the contents
        and placing them in the MathSoc Office.
\end{enumerate}

Any contents that have been removed from a locker at any point during the time
will be labelled and placed in the MathSoc Office for pickup. Belongings shall
not be returned to students without photo identification and will be kept for a
period of 30 days. After this period, all contents will be placed in the lost
and found.

\subsection{Locker Use}
Lockers shall not be used to store items forbidden by law or University policy,
including but not limited to: weapons, any flammable substances, explosive
devices, or illegal substances. Lockers should also not be used to store food,
drink or other perishable items.

MathSoc reserves the right to open any locker thought to be in violation of the
above rule with 24 hours prior notice to the occupier.

MathSoc may remove only items that violate University policy or food, drinks,
and other perishable items. MathSoc may dispose only of food, drinks, and other
perishable items.
