\section{Marketing Policy}

Any MathSoc approved marketing material and resources including posters and MathSoc owned and operated social media accounts must follow the guidelines set in this policy. 

All postings must contain information regarding contact persons or organizations, and event date.
Any postings that are written in a language other than English must contain an English translation. 

\subsection{MathSoc Bulletin Board Policy}

The MathSoc bulletin boards are: 
\begin{itemize}
    \item 2 Bulletin Kiosks in MC 3rd floor Hallway 
    \item MC 3rd floor Glass boards 
    \item 3 bulletin boards next to MC3038 
    \item DC 1st floor main foyer, behind elevator next to the DC fishbowl 
\end{itemize}

The Marketing Directors and the Vice President, Communications are responsible for all notices posted on  MathSoc bulletin boards. 
All notices must be brought to the Society Office and must be approved by the  Vice President, Communications or a marketing director. 
Each approved poster must receive a stamp of Society  approval with a date for removal. 
This date is set at two weeks time from the posting or one day after the  poster's event has finished. 
The notices will be posted until that date. 
Posters can only be posted by the  Postings Director or designate. 
The Postings Director reserves the right to remove and discard posters  which violate this policy. 
Posters sent or delivered to the Society should number no more than 4 if  standard size (8.5x11) or 2 if larger. 

\textbf{Note}: University Policy \# 2 (Bulletin Boards, Temporary Signs and Notices) applies to all posters and  notices. Election Materials may be posted on any surface in MC or DC with masking tape. 

\subsection{Violations and Penalties}

Any posted notices that violate this Policy will be removed and discarded and the posting organization  will be penalized in the following manner: 
\begin{itemize}
    \item First offenses will result in the formal warning of the posting organization or person.
    \item Subsequent offenses shall result in suspension of posting privileges for 2 weeks.
\end{itemize}
