\section{Non-voting resource members}
\emph{effective [at time of ratification]; new}\\

\subsection{Purpose}

There are often occasions where it is valuable to the Board to 
extend membership to non-voting resource members. While some such 
non-voting members are defined elsewhere (e.g. the Council Speaker) 
or externally (e.g. the Dean's Delegate), some have no external reference. 
This procedure provides a central definition for any 
internally-defined non-voting resource members of the Board.

Any additions or removals to the list of non-voting resource members of the Board 
must still be ratified within Bylaw 6.2.

\subsection{Lead, Infrastructure}

\subsubsection{Appointment}

In the event that the Lead, Infrastructure role is vacant, a new 
Lead, Infrastructure shall be appointed by the Board of Directors 
of the Society at the first Board meeting of the term. 

The Lead, Infrastructure should be appointed for a 1-year term.

\subsubsection{Responsibilities}

The Lead, Infrastructure is intended to be the single individual responsible for 
MathSoc's technical infrastructure.

As the primary developer of the MathSoc Website, the Lead, Infrastructure will:
\begin{enumerate}
  \item In coordination with the Website Committee, determine the 
  direction of the new website and the feasibility of new requested functionalities.
  \item Monitor MathSoc infrastructure to ensure continued uptime, especially during high-usage periods 
  \item Support any additional volunteer web developers and content 
  maintainers working on the MathSoc website
  \item Support and enable the Vice President, Communications in making simple 
  content updates to the MathSoc website
\end{enumerate}

Further, as the organization's primary infrastructural point of contact, the Lead, Infrastructure will:
\begin{enumerate}
  \item Support members of Council and Board with infrastructural concerns
  \item Manage lines of communication with external partners, such as IST and MFCF 
  \item Maintain clear documentation and lines of communication to support future Leads, Infrastructure.
\end{enumerate}


