\section{MathSoc Office Rentals}
\emph{effective March 14, 2024}\\

\subsection{Overview}

The MathSoc office hosts rental services to any MathSoc members. Some of these services are the renting of board games, calculators or textbooks. On a number of occasions, the ability to use these services is misused and taken for granted, resulting in items not being returned to the MathSoc office. This policy solidifies the rental policy for items within the MathSoc office.


\subsection{Definitions}
\begin{enumerate}
    \item “Rented item” refers to any item that has been rented by a MathSoc member from the MathSoc office, which may include but is not limited to:
    \begin{enumerate}
        \item Board games,
        \item Calculators, or
        \item Textbooks
    \end{enumerate}
\end{enumerate}

\subsection{Rental Limits}

MathSoc members are limited to having any combination of:
\begin{enumerate}
    \item up to three outstanding board game rentals,
    \item up to one outstanding calculator rental, and
    \item up to three outstanding textbook rentals
\end{enumerate}
Rental limits of other non-textbook items may be placed by the discretion of the Vice President, Operations.

\subsection{Non-Textbook Item Rentals}

Any non-textbook item rented from the MathSoc office by a MathSoc member is required to be returned within 14 days of the rental date.

If the member does not return said item within the given time, all rental privileges will be revoked until the overdue rental item(s) are returned. Depending on circumstances for late return, at the discretion of the VPO, rental privileges may be revoked for set time period or remainder of the term.


The member shall have their rental privileges revoked on a termly basis until all outstanding items are returned to the MathSoc office.

\subsection{Textbook Library Rentals}

Any textbook rented from the MathSoc office by a MathSoc member is required to be returned within 31 days of the rental date.

If the member does not return said textbook within the given time, the member will have their rental privileges revoked from all rental services for the remainder of the term. The member shall be notified by the Vice President, Operations or any other MathSoc Executive about their ban along with a request to return the textbook promptly.

The member shall have their rental privileges revoked on a termly basis until all outstanding items are returned to the MathSoc office.

\subsection{Late Rentals}

If the rental time of an item ends after the last day the MathSoc office is open, the item must instead be returned on the last day of the office being open.

If the item is not returned on the last day of the MathSoc office being open, the member shall have their rental privileges revoked 

If at the Vice President, Operations, or President’s approval, late rentals may be returned after the last day the MathSoc office is open with a date decided upon the Vice President, Operations or President, and the member shall incur no penalty.

\subsection{Monetary Penalty}

If a member has been barred from rental services for two consecutive terms due to the failed return of the same item(s), the member may be charged the full replacement value of the missing item(s).

\subsection{Agreement of Policy}

Upon renting any item from the MathSoc office, the MathSoc member is required to sign a receipt that confirms their agreement of this policy, along with any relevant sanctions that may be imposed if the item is not returned on time. If the receipt is not signed, the rented item will not be given to the member until the receipt is signed and thus agreeing with the procedures followed in this policy.

\subsection{Removal of Rental Ban}

If a MathSoc member is currently barred from rental services from the MathSoc office, there are two ways the ban shall be removed:
\begin{enumerate}
    \item Upon returning all delinquent rental items, the ban will be lifted during the following term, at which point the member may use the rental services as outlined in this policy, or
    \item At any point, subject to the approval of the Vice President, Operations or the President, the ban of any member from rental services provided by the MathSoc office may be lifted.
\end{enumerate}
