\section{Full and Part-time Permanent Staff}
\emph{effective November 28, 2024; replaces August 19, 2018; December 1, 1998; new}\\

\subsection{Definitions}
``Staff'' means Regular Full-Time Staff and Regular Part-Time Staff, as defined
by University Policy 54 (Definition of Staff).

\subsection{Human Resources Committee}
The Human Resources Committee shall consist of:
\begin{enumerate}
    \item The President;
    \item The Vice-President, Operations;
    \item The Chair of the Society;
    \item The Business Manager of the Society;
    \item The President of the Federation of 
        Students, or designate;
    \item A representative of the Office of the Dean of Mathematics, appointed
        by the Dean, to act in a non-voting, advisory capacity; and
    \item A representative of the Department of Human Resources, to act in a
        non-voting, advisory capacity.
\end{enumerate}

The Human Resources Committee shall, on behalf of the President, act as the
Society's department head for the purposes of any and all University policies
regarding Staff.

The Committee shall be empowered to make all decisions regarding the employment
of Staff, including, but not limited to:
\begin{enumerate}
    \item Staff evaluations;
    \item The hiring of new Staff;
    \item Disciplinary actions;
    \item The release of Staff; and,
    \item The job descriptions of Staff.
\end{enumerate}

The Committee shall meet as deemed necessary by Board to address any changes or concerns.

The Committee shall have access to any and all financial records of the Society
that it feels necessary in order to conduct its business.

The Committee shall be a Standing Committee of the Board of Directors.

\subsection{Business Manager Performance Appraisal}
The Business Manager undergoes a Performance Appraisal, hereby referred to as the “evaluation”, every year. 

This evaluation process must be carried out by the President and the Chair of the Board, in collaboration with the Director of Operations and Development of WUSA, hereby referred to as “WUSA Operations”. 

The information collection and evaluation processes outlined in this procedure must align with the University’s HR performance appraisal metrics.

\subsubsection{Termly Information Collection}
Each academic term, the Chair and the President must meet with WUSA Operations before the third regular meeting of the Board of Directors to discuss collecting information regarding the Business Manager’s performance.

Barring special circumstances, the Chair and the President must then anonymously survey the following groups for feedback regarding performance in the term:

\begin{enumerate}
\item{Chair of the Board of Directors;}
\item{Executive Officers;}
\item{Full-time staff of the Coffee and Donut shop;}
\item{Directors who act as Chair or Vice-Chair for the Executive Appointment and Executive Evaluation Committees; and,}
\item{Associate Dean, Undergraduate Studies, or designate.}
\end{enumerate}

Such responses must be strictly confidential and securely sent to WUSA Operations by the final meeting of the Board of Directors in each term.

The President and the Chair may securely send an additional written evaluation of the Business Manager's performance in the term to WUSA Operations by the end of the term.

The Society will not retain documents, responses, or any associated files once WUSA Operations has received them. Only the Chair, the President and WUSA Operations will be able to view such documents unless they determine that there is a specific and identifiable need for a particular individual to access a certain file or a subset of the
information contained therein.

\subsubsection{Winter Term Evaluation}
The Chair and the President in Winter terms must meet with WUSA Operations to initiate the evaluation process no later than February 1. 

Upon initiation of the process, the Chair or the President must inform the Board at its next regular meeting.

The evaluation process shall take into consideration the survey responses from the past year aiming to be a holistic view of performance throughout the year.

The Chair, the President and WUSA Operations shall aim to conclude the process by the end of the term, barring extenuating circumstances.

