\section{Volunteer Mandatory Training}
\emph{effective September 1, 2024; new}\\

\subsection{Overview}

Training modules are courses available on Learn for free self-enrollment. They need only be
completed once and will stay on the student's transcript while they remain a part of the
University community. This procedure states which training modules volunteers in the
Society must complete.

\subsection{Definition of Groups}

The following groups shall be required to complete this training: \\
\\ \textbf{Group A}: The Executive Officers of the Society, the Chair of the Society, and the Speaker.
\\ \textbf{Group B}: The Secretary of the Society and Council Secretary.
\\ \textbf{Group C}: The president and other executives of Clubs under the aegis of MathSoc.
\\ \textbf{Group D}: Event Volunteers under the Vice-President, Internal.
\\ \textbf{Group E}: Office Managers under the Vice-President, Operations.
\\ \textbf{Group F}: Office Staff under the Vice-President, Operations.
\\ \textbf{Group G}: Finance Directors under the Vice-President, Finance.
\\ \textbf{Group H}: Academic Event Volunteers under the Vice-President, Academic.

\subsection{Required Training Modules for Groups}

All groups must complete their required training modules within two weeks of coming into their
position.

\begin{table}[h]
	\resizebox{1.01\textwidth}{!}{
		\centering
		\begin{tabular}{|p{0.3\linewidth}|p{0.22\linewidth}|p{0.21\linewidth}|p{0.20\linewidth}|p{0.19\linewidth}|}
			\hline
			Groups                                                                                        & Employee Safety Orientation (SO1001) & Workplace Violence (SO1801) & Accessibility Training & Cyber Awareness Essentials \\
			\hline
			\textbf{A}: The Executive Officers of the Society, the Chair of the Society, and the Speaker. & \checkmark                           & \checkmark                  & \checkmark             & \checkmark                 \\
			\hline
			\textbf{B}: The Secretary of the Society and Council Secretary.                               &                                      & \checkmark                  &                        & \checkmark                 \\
			\hline
			\textbf{C}: The president and other executives of Clubs under the aegis of MathSoc.           & \checkmark                           & \checkmark                  & \checkmark             & \checkmark                 \\
			\hline
			\textbf{D}: Event Volunteers under the Vice-President, Internal                               & \checkmark                           & \checkmark                  & \checkmark             & \checkmark                 \\
			\hline
			\textbf{E}: Office Managers under the Vice-President, Operations.                             & \checkmark                           & \checkmark                  & \checkmark             &                            \\
			\hline
			\textbf{F}: Office Staff under the Vice-President, Operations.                                &                                      & \checkmark                  & \checkmark             &                            \\
			\hline
			\textbf{G}: Finance Directors under the Vice-President, Finance.                              &                                      & \checkmark                  &                        & \checkmark                 \\
			\hline
			\textbf{H}: Academic Event Volunteers under the Vice-President, Academic.                     &                                      & \checkmark                  & \checkmark             &                            \\
			\hline
		\end{tabular}
	}
\end{table}

\subsection{Verification of Completion of Training}

The Business Manager and the Chair of the Society shall ensure that groups \textbf{A} and \textbf{B}
have completed their training by the required date.
\\ The Vice-President, Internal shall ensure that groups \textbf{C} and \textbf{D} have completed their
training by the required date.
\\ The Vice-President, Operations shall ensure that groups \textbf{E} and \textbf{F} have completed their
training by the required date.
\\ The Vice-President, Finance shall ensure that group \textbf{G} has completed their training by the
required date.
\\ The Vice-President, Academic shall ensure that group \textbf{H} has completed their training by the
required date.
\\ Failure to complete necessary training may result in an individual being removed from their role.

