\section{Website Committee}
\emph{effective July 24, 2024; new}\\

\subsection{Composition and Selection of Members}

The membership of the committee shall be:
\begin{enumerate}
	\item Two (2) current voting members of the Board of Directors;
	\item One (1) current voting member of Council;
	\item At least one (1) lead web developer;
	\item The Vice-President, Communications; and
	\item The Business Manager.
\end{enumerate}

Directors and Councillors shall be appointed by their respective governing bodies.
Lead web developer appointments shall be made by the committee, and ratified by the Board of Directors.
Should a Director or Councillor seat become vacant, the respective governing body shall appoint a replacement at their earliest convenience.

The Board of Directors shall appoint one Director to serve as the Chair of the Committee.
Directors and Councillor(s) who are also lead web developers may sit with a dual mandate, thus satisfying two membership requirements.

All members, with the exception of the Councillor(s) and the Vice-President, Communications, shall serve on the committee for a period of at least eight (8) months or until they leave their position, whichever is first.

\subsection{Meetings}

The committee shall meet at least once a month.
Meetings may be called by the Chair of the Committee, or upon the written request of any two members.

\subsection{Powers and Duties}

The committee shall:

\begin{enumerate}
  \item Provide stable long-term guidance for the overall direction and development of the MathSoc website;
  \item Oversee the hiring and direction of MathSoc’s web developers, in collaboration with the Vice President, Communications;
  \item Hire lead web developers to be primarily responsible for website development;
  \item Manage solicited website feedback and incorporate it into the direction of the website;
  \item Report hiring updates to the Board of Directors by no later than the second Board meeting of every term; and
  \item Report development progress to the Board of Directors at the final Board meeting of every term.
\end{enumerate}

Web developers shall be operationally and administratively overseen by the Vice President, Communications, but are ultimately subordinate to the committee.

Although members may conduct the below activities independently from the committee according to their individual mandates, the committee as a whole shall not:
\begin{enumerate}
  \item Manage website content;
  \item Manage detailed requirements; or
  \item Be involved with the technical implementation of the website.
\end{enumerate}

