\section{Conflict of Interest}
\emph{updated April 2022; replaces May 1st, 2019}

\subsection{Definition}


A representative shall be considered to have an actual, perceived, or potential conflict of interest when the opportunity exists for the representative to use the authority, knowledge, or influence of MathSoc Council or MathSoc Board of Directors, or a committee or body thereof, for individual benefit or to preferentially benefit any individual or organization with whom the representative has a familial, personal, fiduciary, or financial relationship.  

\noindent

A representative is a member of MathSoc Council, an Executive or a Director on the MathSoc Board of Directors. 

\subsection{Certify Expectations}

All representatives shall be expected to certify, prior to candidacy for election or appointment, that if elected they shall fulfil the responsibilities outlined in this procedure. Failure of a candidate to certify the same shall render the individual ineligible for candidacy.

\subsection{Conflict of Interest Declaration}

All representatives will be required to complete and submit a Conflict of Interest Declaration, which will be in congruence with the requirements of this procedure, to the Secretary of Council upon their election or reelection to Council, and/or to the Chair of the Board upon their election or reelection to the Board of Directors. 

\subsubsection{Deadline of Submission}

The form must be submitted no later than the first meeting that a representative is expected to attend of the relevant body of their term.

\subsubsection{Duplication of Forms}

For representatives that are on both the Board of Directors and Council, this form must be submitted to each relevant party. 


\subsubection{Form Accuracy} 

In the event that new conflicts of interests arise during the course of a representative or executive's term, representatives and executives are responsible for ensuring their Conflict of Interest Declaration remains up to date.

\subsection{Availability} 

The Secretary of Council shall ensure that copies of all submitted Conflict of Interest Declarations are available for inspection by any member of MathSoc during any Council meeting. Additionally, the Secretary shall make arrangements upon request for a member of MathSoc unable to attend a Council meeting to instead view the documents (without being able to preserve copies of it) at the MathSoc office.

\noindent 
The Society Secretary shall ensure that copies of all submitted Conflict of Interest Declarations are available for inspection by any member of MathSoc during any Board meeting. Additionally, the Secretary shall make arrangements upon request for a member of MathSoc unable to attend a Board meeting to instead view the documents (without being able to preserve copies of it) at the MathSoc office.


\subsection{Inability to Vote} 

Representatives who have an actual, perceived, or potential conflict of interest, with respect to any matter under consideration by Council, Board, a MathSoc General Meeting, or a committee or body thereof, shall declare the nature and extent of the interest immediately and refrain from taking part in any vote in relation to the matter.

\subsection{Disputes} 

When Council or Board, or a committee or body thereof, is of the opinion that a conflict of interest exists that has not been declared, Council, Board, a MathSoc General Meeting, or the committee or body thereof may declare by resolution, carried by two-thirds of its members present at the meeting, that a conflict of interest exists and the representative thus declared to be in conflict refrain from taking part in any discussion or in any vote in relation to the matter.
