\section{Math Graduation Committee}
Effective August 6, 2020; replaces November 27, 2006.

\subsection{Definition}
The Math Graduation Committee (MGC) shall be a standing committee of the Society, the 
purpose of which shall be to run events, including the Math Graduation Ball, and 
selecting the valedictorian for the graduating undergraduate students of the Faculty 
of Mathematics.

\subsection{Membership}
The voting members of the Committee shall be:
\begin{enumerate}
\item One faculty advisor appointed by the Dean of Mathematics;
\item One or Two Math Graduation Chairs, one that will be graduating in Winter and 
another in Spring term;
\item One Financial Director of the Mathematics Graduation Committee;
\item Members appointed by the Chairs;
\item The Vice-President, Internals of the Society; and 
\item The Business Manager of the Society.
\end{enumerate}
The non-voting members of the Committee shall be:
\begin{enumerate}
\item All graduating members of the Society.
\end{enumerate}

\subsection{Math Graduation Chair}
The Math Graduation Chair shall:
\begin{enumerate}
\item Be picked from the graduating class in the manner described below.
\item Be a voting and social member of the Society to be graduating in the Fall, 
Winter term and/or Spring term;
\item Report to the Executive Team and the Business Manager; and 
\item Step down after transitioning their successor on the Spring term.
\end{enumerate}

\subsection{Financial Director}
The Financial Director shall:
\begin{enumerate}
\item Be appointed by the Chair;
\item Be responsible to the Chair;
\item Share all financial records with the Business Manager and the VP, Finances of 
the Society; and
\item Maintain all financial records of the Committee.
\end{enumerate}

\subsection{Funding}
Each term, the Society shall set aside at least one thousand dollars (\$1000) for the use of the Math Graduation Committee in its budget.

\subsection{Signing Authority}
Committee signing authority shall reside with the Chair(s), the Financial Director, 
and the Vice-President, Finances. In order to authorize a reimbursement, the Chair(s) 
or Financial Director needs to notify the Vice-President, Finances of the expense 
ahead of time. If the expenses are not in the budget, the signing authorities should 
follow regular MathSoc club procedures. 

\subsection{Appointment of the Chair}
\subsubsection{General}
Each Chair of the Committee is to finalize their degree in the Spring or Winter term 
when they will be Chair.

\subsubsection{Procedure}
An application for the next Chair(s) shall be publicized in the Spring term, but if 
nobody was found to be qualified these can be carried over to the Fall term. If there 
is no Chair appointed by the beginning of the Winter term, then Council shall appoint 
a Chair for the Committee.

Applicants shall be interviewed by the departing Chair(s), the Business Manager, 
or the Faculty Advisor, and one other Committee Member.
When the new Chair(s) are selected, they shall be ratified by Council.

\subsection{Transition of Chairs}
The outgoing Chair(s) shall meet with the incoming Chair(s) for a transition 
meeting to discuss the transition documentation and the procedures for next year. The 
meeting shall be online or in-person.

In the event no chair is chosen, the VPI shall fill that role.
