\section{Provision and Reimbursement of Alcohol}
\emph{effective November 21, 2019}\\
\paragraph{}

Those hosting events with alcohol will follow relevant standing policies by the University of Waterloo Secretariat (University of Waterloo Policy 21) and the Federation of Students (Feds) Policies and Procedures (Feds Board of Directors Procedure 14).
\paragraph{}
Reasonable use of alcohol for events shall be considered that which:
\begin{enumerate}
\item Follows all UW and Federation of Students policies in regards to promotion and consumption of alcohol;
\item Follows all laws of the province of Ontario and Canada regarding the consumption and provision of alcoholic beverages;
\item Is not the primary or sole focus of the event;
\item Alcohol is not the sole beverage option: other beverages must be offered and made available for reimbursement to those in attendance; and
\item Is limited to a minority of offered events.
\end{enumerate}

The use of student fees to reimburse alcohol for non-student participants at student focused events is permitted, if approved by the President and the Vice President Finance, and reimbursement of alcohol for student consumption has already been approved for the event (eg. reimbursement for professors at Party with Profs is an acceptable use of society funds).

The reimbursement for student purchase and consumption of alcohol at society events is restricted to that which complies with the policies and procedures herein established, and is pre-approved by the MathSoc Council (or in the absence or inability of the Council the unanimous agreement of the Vice President Finance, President, and Vice President Internal). The “pre-approval” process for the reimbursement of alcoholic beverage expenses at any society event shall constitute a simple majority vote in the affirmative by a properly constituted meeting of the MathSoc Council \textit{prior} to the event.

Organizers of any Society events, including any subsidiaries (clubs) of the society,  who seek reimbursement for alcohol expenses must notify the Speaker of Council, President, VPF, and VPI at least one (1) week prior to the event date. The Speaker of Council, or any agent thereof, shall not include any petition for \textit{post hoc} alcohol expense reimbursement approval on the MathSoc Council agenda; and shall rule any vote on the matter under New Business out of order while this policy is in place. 

All society events, or events of subsidiaries thereof, if providing alcoholic beverages must provide alternatives for those students who cannot or choose not to consume alcohol.
