\section{Capital Improvements Fund}
effective December 6, 2011; replaces July 5, 2010

\subsection{Purpose}
The purpose of the Capital Improvements Committee (hereafter referred to as the Comittee) shall be to fund lasting capital improvements to student space in the Math Faculty, as well as any special project funds allocated by Council.

\subsection{Composition}
The Capital Improvements Fund Committee (the Committee) shall be formed each Winter term or when Council allocates a special project fund, composed of:
\begin{enumerate}
\item The President, who will act as Chair and only vote to break ties.
\item The Vice President, Operations.
\item The Vice President, Finances.
\item Three voting members of Council, as appointed by Council.
\item A representative of the Dean's Office, non-voting.
\end{enumerate}

\subsection{Fund}
The Fund will be composed of two parts:
\begin{enumerate}
\item The principle portion, which:
	\begin{enumerate}
	\item Will be administered by the Vice President, Finances
	\item Will be invested in an interest-bearing vehicle
	\item Is not available to be spent 
	\end{enumerate}
\item The current portion, which:
	\begin{enumerate}
	\item Will be composed of the student fee contributions and interest on the principle portion from the preceding Spring and Fall terms as well as the current Winter term. 
	\item Is the amount that may be allocated to expenditures. 
	\end{enumerate}
\end{enumerate}
Each term, seventeen and a half percent (17.5\%) of the student fee for each fee paying member of the Society shall be allocated to the Fund, seventy-five percent of which shall be allocated to the current portion of the Fund and twenty-five percent to the principle portion of the fund.\\
Donations to the Fund may be dedicated to either the current or principle portion of the Fund, in any combination, at the discretion of the donor.\\
Any amount of the current portion that is unallocated at the beginning of the Spring term will be transferred to the principle portion of the Fund.\\
Funds that remain unspent one year after they have been allocated become unavailable and are transferred to the principle portion.\\

\subsection{Special Project Funds}
From time to time Council may allocate funds for special projects. These allocations are to be distributed in the same manner as the current portion of the Capital Improvements Fund, except that there is no requirement that unspent funds be contributed to the principle portion.
Additionally, Council may outline a new funding priority for any special project fund as an alternative to section 5.

\subsection{Priority of Funding}
At the discretion of the committee, proposals shall be given priority in the following decreasing order:\
\begin{itemize}
\item Improvements to Society offices, Lounges and the Math Coffee and Donut Shop.
\item Improvements to the offices of recognised Clubs
\item Improvements to the offices of affiliates including mathNEWS, Math Graduating Committee, and Math \item Orientation Committee.
\item Other projects that the committee feels fulfill the purpose of the Fund
\end{itemize}


\subsection{Procedure}
Appropriate application forms shall be made available no later than the end of January for use of the Fund and as soon as possible after Council allocates a special project fund. The deadline for submission of proposals to the President shall be the later of the end of January or 10 business days after applications were made available.
The President shall assemble and distribute a package of the submissions to the Committee.
The Committee will hold meetings in two parts:
\begin{itemize}
\item Entertain presentations for each proposal.
\item Allocate some or all of the available funds in a report to Council.
\end{itemize}
The report of the Committee is subject to ratification but not modification by Council. In the event that Council does not ratify the report of the Committee, the committee may reconvene in order to produce a new report.
