\section{Electronic Communication}
effective December 4, 2002; replaces March 25, 1996

\subsection{Newsgroups}
The society recognizes the following two newsgroups for the purposes described below.
The newsgroup uw.math.ugrad exists for undergraduate mathematics students to discuss general issues and concerns. It also provides a forum for Society announcements, and a mechanism for feedback.
The newsgroup uw.math.mathsoc exists as a communication channel between Society volunteers. Posts should be restricted to operational concerns of the Society; i.e. announcements of Board meetings, training sessions, etc.

\subsection{MathSoc Mailing Lists}
The Society may in its operations make use of mailing lists to aid in the operations of the Society. Messages to the mailing list should be restricted to the mandate of the mailing list. The operator of a MathSoc mailing list may take action to ensure that all use of the mailing list is restricted to its mandate.

\subsection{MFCF Mailing List}
The Society has available to it the use of a mailing list for all undergraduate students registered in the Faculty of Mathematics, administered by MFCF. The following restrictions apply to messages sent via this mailing list:
All messages must be approved by the President before being submitted for distribution.
All messages being submitted for distribution must include a note at the end of the message giving instructions to students on how to unsubscribe from the list.
Not more than 2 messages to all undergraduate students shall be sent in any one month period.
No student should receive more than three messages in any one month period.
Not more than 5 messages shall be sent in any one month period.
In addition, messages sent via the mailing list must accommodate any requirements of the Dean’s Office or MFCF. In particular, MFCF requires three business days from the submission of a message to its distribution.