\section{Executive Evaluation Criteria}

The following table shall be used as a standard list of metrics to evaluate the Executives.\\
\\
\begin{longtable}{p{0.2\linewidth} p{0.75\linewidth}}
\toprule
Executive & Metrics\\
\midrule
All Executive &
\begin{itemize}
\item Acts as a positive representative for the Society, upholding ethical behaviour and being respectful and mindful of others.
\item Submits a report and attends Council meetings.
\item Submits a report and attends Board meetings.
\item Attends meetings with the Executive team.
\item Submits a report and attends termly General Meeting.
\item Attends most committee meetings of which they are a member.
\item Attends any meetings with the Dean and Associate Dean, as part of the Executive team (unless unavailable).
\item Communicates well with the rest of the Executive team.
\item Maintains office hours or is otherwise regularly available to students.
\item Makes best effort to attend “core” MathSoc events (e.g. Party with Profs, Pi Day, etc.).
\item Ensures that volunteers are selected and trained for their duties and in accordance to Board Procedure 19.
\item Ensures that all incoming communication is responded to in a timely manner.
\item Attends transition meeting coming into the appointed position.
\item Attends transition meeting and provides transition notes for new Executive upon exiting the position.
\item Provides self-evaluation to Business Manager at the end of their term.
\item Carries out decisions of the Society, such as those made by Council and the Board, in their capacity.
\end{itemize}
\\
\midrule
President &
\begin{itemize}
\item Represents the Society at official functions and public occasions.
\item Represents the Society and its members to other organizations.
\item Works with external organizations on behalf of the Society.
\item Attends regular meetings of the WUSA Committee of Presidents.
\item Must run a general meeting, following all relevant bylaws, that is well advertised, organized, and attended.
\item Sends out regular communication to all students via mass email, in collaboration with the VP Communications.
\item Meets with the WUSA President during their term.
\item Coordinates meetings with the Dean, Associate Dean and other Faculty members for the Executive team.
\item Coordinates regular meetings with the Executive team.
\item Ensures smooth transition between Executive teams.
\item Works closely with the Business Manager to ensure termly goals are met and long-term objectives carry forward.
\item Fosters a welcoming and collaborative environment between all areas of the Society, mediating conflict when needed.
\item Makes an effort to ensure that all areas of the Society transition smoothly to the next term, with relevant transition documentation updated.
\end{itemize}
\\
\midrule
Vice President, Finance &
\begin{itemize}
\item Prepares a budget for the term and ensures the Budget Package gets approved by Council and WUSA in a timely manner based on the policies, procedures and bylaws.
\item Ensures Finance Directors are hired and properly trained.
\item Ensures that clubs and services receive reimbursements in a timely manner.
\item Tracks Club's budget expenditures and ensures that Clubs remain within their budget.
\item Completes budget to actual expenditures on a termly basis for Clubs and Executives and ensures the Master Budget is up to date.
\item Collects Club's termly Signing Authority, membership list and fees, and any Club’s sales or other revenue.
\item Enforces proper cash handling practices for the Society.
\item Ensures that the MathSoc Office cash drawer is appropriately managed every day.
\item Presents a financial report at the General Meeting for both MathSoc and CnD.
\item Meets regularly with the WUSA Societies Accountant.
\item Meets regularly with the Business Manager to ensure proper accounting procedures are kept in place and new procedures are added as necessary.
\end{itemize}
\\
\midrule
Vice President, Operations & 
\begin{itemize}
\item Oversees the services provided by the Society.
\item Oversees the Society office.
\item Meets regularly with the Office Managers and Office Workers.
\item Ensures Office Managers/Workers are properly trained.
\item Ensures MathSoc Office has consistent hours of operation and is properly staffed throughout the day.
\item Ensures all online MathSoc services are working properly in collaboration with the VP Communications.
\item Ensures lockers are available for sign-out at the start of each term and manages leftover contents in accordance with Board Procedure 6.
\item Ensures MathSoc Office inventory is up to date and replenished accordingly.
\item Ensures board game rentals are managed properly and manages the acquisition of new board games as required.
\item Ensures equipment and room bookings are handled in a timely manner.
\item Ensures that all areas of the MathSoc Office are clean and well organized.
\end{itemize}
\\
\midrule
Vice President, Internal &
\begin{itemize}
\item Oversees appreciation of all volunteers of the Society.
\item Oversees all internal organizations on behalf of the Society, including Clubs and Affiliates.
\item Meets with every Club/Affiliate Executive at least once each term.
\item Ensures that volunteers within the Society are appropriately recognized for their efforts and services.
\item Coordinates the acquisition of new board games as needed, in collaboration with the VP Operations.
\item Ensures that event forms are submitted for all MathSoc Events in a timely manner.
\item Informs clubs/affiliates how to complete event forms and ensures that they are submitted in a timely manner.
\item Plans Semi-formal [Spring and/or Fall term only, if applicable].
\item Assists and oversees Math Graduation Committee as needed.
\item Runs a Welcome Week and Clubs Day at the start of term.
\item Runs Party with Profs (or equivalent).
\item Runs Pi Day (or equivalent).
\item Runs Mental Health/Destress event.
\item Encourages members to become more involved in the Society and ensures that the opportunity exists for them to do so.
\end{itemize}
\\
\midrule
Vice President, Academic &
\begin{itemize}
\item Represents the Society and its members to the Faculty, to the University, and to WUSA on academic issues by adhering to feedback received from students.
\item Ensures that members have access to up-to-date academic information.
\item Run at least two academic events of some sort per term.
\item Reports to Council with updates on academic meetings.
\item Solicits student feedback and communicates regularly with program reps on Council regarding any updates and changes and student concerns.
\item Meets with the Associate Dean at least once a term.
\item Attends (or sends alternates to) all meetings of the Undergraduate Affairs Committee.
\item Attends (or sends alternates to) all meetings where a Math academic representative should be in attendance.
\item Maintains textbook library and adds directly related resources as necessary.
\item Maintains exam bank and provides updates and related resources when available.
\end{itemize}
\\
\midrule
Vice President, Communications &
\begin{itemize}
\item Provides advertising for all MathSoc events through social media and poster advertisement.
\item Ensures posters are posted in a timely manner and posting boards are kept up to date.
\item Sends out regular communication to all students in collaboration with President, including mass emails.
\item Maintains and updates website in collaboration with the website committee and the VP Operations.
\item Runs outreach initiatives to promote the Society and volunteerism.
\item Draft occasional statements representing the position of the Society on certain matters.
\end{itemize}
\\
\bottomrule
\end{longtable}
