\section{Math Graduation Committee}
Effective November 27, 2006; replaces December 4, 2002

\subsection{Definition}
The Math Graduation Committee (MGC) shall be a standing committee of the Society, the purpose of which shall be to run events, including the Math Grad Ball, for the graduating members of the Society.

\subsection{Membership}
The voting members of the Committee shall be:
\begin{enumerate}
\item One faculty advisor appointed by the Dean of Mathematics;
\item One Math Graduation Chair in the Spring and Fall terms, two in the Winter term;
\item One Financial Director of the Mathematics Graduation Committee; and
\item The Society Vice-President, Finances.
\end{enumerate}
The non-voting members of the Committee shall be:
\begin{enumerate}
\item The Math Graduation Chair in an off-term, if any; and
\item All graduating members of the Society.
\end{enumerate}
The members of the Executive Board shall be:
\begin{enumerate}
\item The Math Graduation Committee Chair or chairs;
\item The Math Graduation Committee Financial Director; and
\item All appointed Directors of the Math Graduation Committee.
\end{enumerate}

\subsection{Math Graduation Chair}
The Math Graduation Chair shall:
\begin{enumerate}
\item Be picked from the graduating class in the manner described below.
\item Be a voting and social member of the Society for at least eight months during the academic year deemed to be the graduating year; four of these months must be the Winter term in which the class graduates.
\item Report to and be responsible to Council.
\item Choose non-voting members of the Committee to serve as Directors of the various events planned throughout the year.
\item Choose one member of the non-voting members of the Committee to be the Financial Director.
\end{enumerate}

\subsection{Financial Director}
The Financial Director shall:
\begin{enumerate}
\item Be appointed by the Chair each term,
\item Be responsible to the Chair, and
\item Maintain all financial records of the Committee.
\end{enumerate}

\subsection{Funding}
Each term, the Society shall set aside at least one thousand dollars (\$1000) for the use of the Math Graduation Committee in its budget.

\subsection{Signing Authority}
Committee signing authority shall reside with the Chair(s), the Financial Director, and the Vice-President, Finances. Two of the above shall be required to endorse each cheque.

\subsection{Merging of Streams}
In the Winter term of the academic year deemed to be the graduating year, the Committees which had been operating as two different units (one per stream) shall become one unit.
The Chairs shall share the responsibilities as co-chairs.
One Financial Director shall be chosen.

\subsection{Appointment of the Chair}
\subsubsection{General}
The Chair for the Committee whose penultimate term is the Spring term shall be chosen in the previous Fall term.
The Chair for the Committee whose penultimate term is the Fall term shall be chosen in the previous Winter term.
\subsubsection{Procedure}
\begin{itemize}
\item Nominations
	\begin{itemize}
	\item Nominations for the position shall be opened no sooner than the eighth week and no later than the tenth week of the appropriate term. A nominee shall be required ten signatures of members of the graduating class for which the Committee is being struck.
	\item Nominees will meet with the current Committee executive for an information gathering session.
	\item Nominees will meet with Council for a question and answer session followed by a vote by Council to determine which candidates are suitable. Council has the option to decide that there is no suitable candidate, in which case nominations are re-opened (as above).
	\item If Council determines that there is only one suitable candidate, that candidate shall be acclaimed to the position immediately.
	\item If Council determines that there is more than one suitable candidate, an election shall be held to determine which suitable candidate shall be the Chair.
	\end{itemize}
\item Campaigning
	\begin{itemize}
	\item The campaign period shall begin no later than one business day after the vote by Council.
	\item The campaign shall last for six business days.
	\item Campaign spending limits are to be \$75.00
	\end{itemize}
\item Voting
	\begin{itemize}
	\item All members of the Society who are both voting and social members intending to graduate in the following year shall have one vote.
	\end{itemize}
\end{itemize}
Except where specifically stated above the election will be carried out in the manner determined by the Elections Policy.
In the event no chair is chosen, the President shall fill that role.